### 2016-05-23 intro.tex
adding note about Bloom filters with secret keys, in practice

\section{Introduction}
\paragraph{Basic issues in Naor-Yogev. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won't scale in common network applications
\item The main results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters! \tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.}
\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret. (No matter if the [NY] syntax does or does not allow them to be encoded in the representation.)  This is odd and does not match reality, e.g. the popular Squid proxy uses plain MD5, splits the output into four chunks, and defines these as four hash functions.  Hardly secret.
\item The ``unsteady representation'' does not seem well founded.  Not sure what Bloom filter-like data structures would have randomized querying procedures.  They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.  But what's the purpose of this, if the security definition gives the adversary the set~$S$?  (What are you keeping private?) 
\end{itemize}

>>>>

\section{Introduction}
\paragraph{Basic issues in Naor-Yogev. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won't scale in common network applications
\item The main results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters! \tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.}
\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret. (No matter if the [NY] syntax does or does not allow them to be encoded in the representation.)  This is odd and does not match reality, e.g. the popular Squid proxy uses plain MD5, splits the output into four chunks, and defines these as four hash functions.  Hardly secret. \tsnote{I did find a setting where Bloom filters use secret keys: privacy-preserving record linkage.  Here one wants to know if two databases contain information about the same person (abstractly, a set of record identifiers).  Suggested hash functions are $H_j(x) = g(x) + j\cdot h(x) \bmod m$ for $j=\{0,1,\ldots,k-1\}$, and $g,h$ are (e.g.) HMAC-SHA1 with different keys.  In practice, apparently the~$x$ are bigrams extracted from string identifiers (e.g. ``Thomas''); papers show how to break this ``encrypted'' Bloom filter by recovering a large fraction of names, via (roughly) frequency analysis.}
\item The ``unsteady representation'' does not seem well founded.  Not sure what Bloom filter-like data structures would have randomized querying procedures.  They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.  But what's the purpose of this, if the security definition gives the adversary the set~$S$?  (What are you keeping private?) 
\end{itemize}
